---
title: "WUP_04"
author: "Precious Calderon"
date: "Summer 2022"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(knitr)
require(tidyverse)
require(tigerstats)

mydata <- read_csv(file = "GSScsv.csv")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

The data is in the file GSScsv.csv and came from the 2018 General Social Survey.  The question to answer is to resolve this hypothesis.  
$H_0$ There is no difference between the average score on the WORDSUM test and level of schooling DEGREE  
$H_a$ There is a significant difference in average score on the WORDSUM test between at least two levels of DEGREE  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
  
```{r}
basicCN <- ggplot(mydata,aes(x=DEGREE,y=WORDSUM))
```{r}
basicCN + geom_boxplot()
```
  
The median Wordsum score of people with a graduate degree is the highest among all other degree holders. Meanwhile, the interquartile range (box) of the Wordsum scores of high school graduates is the lowest among all the degree holders. The median scores of bachelor and junior college degree holders are about the same, but the box for the former is higher than the latter. Graphically, we can see that people with a graduate degree generally score better than people with other types of degree.
  
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
  
```{r}
favstats(WORDSUM~DEGREE,data=mydata)
```
  
The table above shows that people who have a graduate degree have the highest average wordsum score with a mean value of 10 points. Meanwhile, junior college degree holders obtained an average of 9.9 points. Bachelor degree holders follows suit with an average of 9.2 points along with high school degree holders with 8.2 points. Lastly, LT high school degree holders achieved the lowest average score at 7.75 points. 
  
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
  
```{r}
model1 <- aov(WORDSUM~DEGREE,data=mydata)
summary.aov(model1)
```
    
The p-value of 0.000236 is small enough to to show tat there is no similarity in categories of data. 
  
```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3, 15.7, 2, 2))
plot(TukeyHSD(model1),las=2)
```
  
The wordsum scores of high school and graduate degree holders are different because the confidence level interval does not cross the zero mark. Similarly, lt high school and graduate  degree holders score differently on wordsum  because the confidence level range does not cross the zero mark.  
  

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
  
Based on the graphical, numerical, and inferential results, we found out that people who have different degrees score differently on wordsum. Moreover, graduate degree holders score the highest on wordsum while lt high school degree holders score the lowest. Therefore, we can reject the null hypothesis which claims that there is no difference between the average score on the WORDSUM test and level of schooling DEGREE.    